---
title: "fit_nest_survival"
author: "Randall Friendly"
date: "`r Sys.Date()`"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r setup, include=FALSE}
# the first code chunk is usually for loading packages and setting formatting things, if needed
###Load packages to run NS models
library(RMark)
library(tidyverse)
library(readr)
library(msm)
library(ggplot2)
library(data.table)

# set current date
today<-Sys.Date()

```

## Introduction
This analysis fits nest survival models in the RMark package. The models examine variation in daily nest survival rate of Spectacled Eiders nesting at Kigigak Island and Utqiagvik.

First, load data.

```{r load data}
###Load the SPEI data INP file
spei_data<- read.csv("nest_survival/data/INP_20220921.csv", header = TRUE)
```
Date file includes data from 2 sites and X years.

Next, wrangle data to prepare for fitting models.

```{r wrangle data}
###Check the headers. Sometimes column name changes when reading csv files. 
head(spei_data)
summary(spei_data)

###Make year a factor variable
is.factor(spei_data$Year)
spei_data$Year<-as.factor(spei_data$Year)
is.factor(spei_data$Year) #it is now a factor variable

###Make Site a factor variable
is.factor(spei_data$Site)
spei_data$Site<-as.factor(spei_data$Site)
is.factor(spei_data$Site) #now a factor variable

###Square the sea ice variables. (Quadratic term and effect). This is adding another column.
spei_data$Win_Hi2<-spei_data$Win_Hi^2
spei_data$Win_Lo2<-spei_data$Win_Lo^2
spei_data$Spr_Hi2<-spei_data$Spr_Hi^2
spei_data$Spr_Lo2<-spei_data$Spr_Lo^2
head(spei_data) #these two columns are now in the dataframe
```

Next fit models with temporal explanatory variables.

```{r fit model set 1}
#fit nest survival models with taking away the intercept and using initial values
##### NEST SURVIVAL #####
### From 1994-2021 the earliest julian start day is 134 and the latest is 209. 
### I am taking the difference between these two to get the nesting season for all years (nocc). equals 75
###Nest Survival covariate
run.modelst = function()
{
  # 1. constant daily survival rate model (null)
  S.dot = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.dot",
               model.parameters = list(S=list(formula = ~ 1)))
  
  # 2. site + year
  S.sy = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sy", groups = c("Site","Year"),
              model.parameters = list(S=list(formula = ~ Site + Year))) 
  
  # 3. site + year + init
  S.syi = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syi", groups = c("Site","Year"),
               model.parameters = list(S=list(formula = ~ Site + Year + Init)),
               initial = S.sy)
  
  # 4. site + year + nestage
  S.syn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syn", groups = c("Site","Year"),
                model.parameters = list(S=list(formula = ~ Site + Year + NestAge)),
                initial = S.sy)
  
  # 5. site + year + init + nestage
  S.syin = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syin", groups = c("Site","Year"),
                 model.parameters = list(S=list(formula = ~ Site + Year + Init + NestAge)),
                 initial = S.syi)
  
  # 6. site + year + init + site * init
  S.syi.sxi = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syi.sxi", groups = c("Site","Year"),
                   model.parameters = list(S=list(formula = ~ Site + Year + Init + Site*Init)),
                   initial = S.syi)
  
  # 7. site + year + nestage + site * nestage
  S.syn.sxn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syn.sxn", groups = c("Site","Year"),
                     model.parameters = list(S=list(formula = ~ Site + Year + NestAge + Site*NestAge)),
                     initial = S.syn)
  
  # 8. site + year + init + nestage + site * init
  S.syin.sxi = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syin.sxi", groups = c("Site","Year"),
                     model.parameters = list(S=list(formula = ~ Site + Year + Init + NestAge + Site*Init)),
                     initial = S.syin)
  
  # 9. site + year + init + nestage + site * nestage
  S.syin.sxn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syin.sxn", groups = c("Site","Year"),
                      model.parameters = list(S=list(formula = ~ Site + Year + Init + NestAge + Site*NestAge)),
                      initial = S.syin)
  
  # 10. site + year + init + nestage + site * init + site * nestage
  S.syin.sxi.sxn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.syina.sxi.sxna", groups = c("Site","Year"),
                          model.parameters = list(S=list(formula = ~ Site + Year + Init + NestAge + Site*Init + Site*NestAge)),
                          initial = S.syin.sxi)
  
  # 11. site * year
  S.sxy = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy", groups = c("Site","Year"),
               model.parameters = list(S=list(formula = ~ -1 + Site:Year)))
  
  # 12. site * year + init
  S.sxy.i = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.i", groups = c("Site","Year"),
                 model.parameters = list(S=list(formula = ~ -1 + Site:Year + Init)),
                 initial = S.sxy)
  
  # 13. site * year + nestage
  S.sxy.n = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.n", groups = c("Site","Year"),
                  model.parameters = list(S=list(formula = ~ -1 + Site:Year + NestAge)),
                  initial = S.sxy)
  
  # 14. site * year + site * init
  S.sxy.sxi = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.sxi", groups = c("Site","Year"),
                   model.parameters = list(S=list(formula = ~ -1 + Site:Year + Site:Init)),
                   initial = S.sxy)
  
  # 15. site * year + site * nestage
  S.sxy.sxn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.sxn", groups = c("Site","Year"),
                    model.parameters = list(S=list(formula = ~ -1 + Site:Year + Site:NestAge)),
                    initial = S.sxy)
  
  # 16. site * year + init + nestge
  S.sxy.in = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.in", groups = c("Site","Year"),
                   model.parameters = list(S=list(formula = ~ -1 + Site:Year + Init + NestAge)),
                   initial = S.sxy.i)
  
  # 17. site * year + init + nestage + site * init
  S.sxy.ina.sxi = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.ina.sxi", groups = c("Site","Year"),
                       model.parameters = list(S=list(formula = ~ -1 + Site:Year + Init + NestAge + Site:Init)),
                       initial = S.sxy.in)
  
  # 18. site * year + init + nestage + site * nestage
  S.sxy.ina.sxn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.ina.sxn", groups = c("Site","Year"),
                        model.parameters = list(S=list(formula = ~ -1 + Site:Year + Init + NestAge + Site:NestAge)),
                        initial = S.sxy.in)
  
  # 19. site * year + init + nestage + site*init + site*nestage
  S.sxy.in.sxi.sxn = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.sxy.in.sxi.sxn", groups = c("Site","Year"),
                            model.parameters = list(S=list(formula = ~ -1 + Site:Year + Site:Init + Site:NestAge)),
                            initial = S.sxy.sxi)
  
  
  
  # Return model table and list of models
  
  return(collect.models())
}

# Fit models
model.resultst=run.modelst()

# Look at model results
model.resultst
magicoutout <- model.resultst

##to look at specific model output
#write the model in the console
model.resultst$S.dot #1
model.resultst$S.sy #2
model.resultst$S.syi #3
model.resultst$S.syn #4
model.resultst$S.syin #5
model.resultst$S.syi.sxi #6
model.resultst$S.syn.sxn #7
model.resultst$S.syin.sxi #8
model.resultst$S.syin.sxn #9
model.resultst$S.syin.sxi.sxn #10
model.resultst$S.sxy #11
model.resultst$S.sxy.i #12
model.resultst$S.sxy.n #13
model.resultst$S.sxy.sxi #14
model.resultst$S.sxy.sxn #15
model.resultst$S.sxy.in #16 top model w=0.42
model.resultst$S.sxy.ina.sxi #17
model.resultst$S.sxy.ina.sxn #18 2nd top model w=0.20
model.resultst$S.sxy.in.sxi.sxn #19

###All the above models ran completely. I checked every model output and the they looked alright.
# There were no funky standard errors or CIs on the Beta estimates

###Write the results output into excel (csv)
sp_temp_modeloutput1 <- model.resultst$model.table
write.csv(sp_temp_modeloutput1, "nest_survival/output/sp_temp_modeloutput1.csv")
```

Next fit models with best supported temporal x-vars in models supported in previous studies.


```{r fit model set 2}
### NEST SURVIVAL ###
### Here I am taking the best supported covariates from stage 1 and incorporating them to best adult survival models from
### previous papers
run.modelst2 = function()
{
  # 1. constant 
  S.dot = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.dot",
               model.parameters = list(S=list(formula = ~ 1)))
  
  # 2. sxt + sxw + winhi + init + nestage + site
  S.stswwhins = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.stswwhins", groups = "Site",
                    model.parameters = list(S=list(formula = ~ sxt + sxw + Win_Hi + Init + NestAge + Site)))
  
  # 3. sxt + sxw + winhi + winhi2 + init + nestage + site
  S.stswwhwh2ins = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.stswwhwh2ins", groups = "Site",
                       model.parameters = list(S=list(formula = ~ sxt + sxw + Win_Hi + Win_Hi2 + Init + NestAge + Site)))
  
  # 4. ice.severity.index + init + nestage + site
  S.wsiins = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.wsiins", groups = "Site",
                 model.parameters = list(S=list(formula = ~ wsi + Init + NestAge + Site)))
  
  # 5. winhi + winhi2 + init + nestage + site
  S.whwh2ins = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.whwh2ins", groups = "Site",
                   model.parameters = list(S=list(formula = ~ Win_Hi + Win_Hi2 + Init + NestAge + Site)))
  
  # 6. winhi + init + nestage + site
  S.whins = mark(spei_data, nocc = 75, model = "Nest", model.name = "S.whins", groups = "Site",
                model.parameters = list(S=list(formula = ~ Win_Hi + Init + NestAge + Site)))
  # Return model table and list of models
  
  return(collect.models())
}

# Fit models
model.resultst2=run.modelst2()

model.resultst2

##to look at specific model output
#write the model in the console
model.resultst2$S.dot
model.resultst2$S.stswwhins # 2nd top model w=.1
model.resultst2$S.stswwhwh2ins # top model w=0.899
model.resultst2$S.wsiins
model.resultst2$S.whwh2ins
model.resultst2$S.whins


###Write the results output into excel (csv)
sp_temp_modeloutput2 <- model.resultst2$model.table
write.csv(sp_temp_modeloutput2, "nest_survival/output/sp_temp_modeloutput2.csv")


###Add top model to the environment with simple name
topmodel <- model.resultst2$S.stswwhwh2ins


###Look at data statistics summary to see what the ice values are.
summary(spei_data)
##Win_Hi: min=0   max=79
##Win_Hi2: min=0   max=6241
##sxt: min=0   max=7
##sxw: min=0   max=5
```

Plot some results. 

```{r create plots}
####GRAPH THE QUADRATIC EFFECT OF HIGH ICE CONDTITIONS
w2fc <- find.covariates(topmodel, spei_data)

###assign appropriate nest ages
w2fc$value[c(741:764, 815:838)] <- 1:24

###assign high ice days range (0:79) to winter days
w2fc$value[c(297:370, 371:444)] <- seq(0, 79, length = 74)

##***create a vector of 0:79 and then create another vector
##* of those squared. (both 74 values)
highdays <- seq(0, 79, length = 74)
highdays2 <- highdays^2

###assign high ice days range (0:79) to winter days
w2fc$value[c(445:518, 519:592)] <- highdays2

###create a design matrix with the values you just changed above
w2design <- fill.covariates(topmodel, w2fc)

###Obtain real estimates
w2.survival <- compute.real(topmodel, design = w2design)

###Insert number of high ice days
w2.survival$high_ice_days[c(1:74, 75:148)] <- seq(0, 79, length = 74)

###Add site for group variable
w2.survival$Site[1:74] <- ("Kigigak Island")
w2.survival$Site[75:148] <- ("Utqia치vik")

###Change column names
colnames(w2.survival) <- c("dsr", "se", "lci", "uci","fixed", "Win_Hi2", "Site")

###Make site a factor variable
is.factor(w2.survival$Site)
w2.survival$Site<-as.factor(w2.survival$Site)
is.factor(w2.survival$Site) #now a factor variable

###Graph the best supported model for high ice days
library(ggplot2)

ggplot(w2.survival, aes(x = Win_Hi2, y = dsr, color = Site)) +
  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = 0.13) +
  geom_line() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = c(0.75, 0.3)) +
  xlab("Extreme High Ice Days") + ylab("Daily Nest Survival Probability") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
ggsave("nest_survival/output/figures/high_ice2.jpg",width = 8, height = 6, dpi = 220)


####Plot spring extreme temp
#Summary
#sxt: min=0 max=7
#sxw: min=0 max=5

spfc <- find.covariates(topmodel, spei_data)
spfc$value[c(741:764, 815:838)] <- 1:24

###assign sxt values 0:7
spfc$value[c(1:74, 75:148)] <- seq(0, 7, length = 74)

###assign sxw values 0:5
#spfc$value[c(149:222, 223:296)] <- seq(0, 5, length = 74)

###create a design matrix with the values you just changed above
spdesign <- fill.covariates(topmodel, spfc)

###Obtain real estimates
sp.survival <- compute.real(topmodel, design = spdesign)

###Insert number spring extremes
sp.survival$spring_extreme[c(1:74, 75:148)] <- seq(0, 7, length = 74)

###Add site for group variable
sp.survival$Site[1:74] <- ("Kigigak Island")
sp.survival$Site[75:148] <- ("Utqia치vik")

###Change column names
colnames(sp.survival) <- c("dsr", "se", "lci", "uci","fixed", "spring_extreme_temp", "Site")

###Make site a factor variable
is.factor(sp.survival$Site)
sp.survival$site<-as.factor(sp.survival$Site)
is.factor(sp.survival$Site) #now a factor variable

ggplot(sp.survival, aes(x = spring_extreme_temp, y = dsr, color = Site)) +
  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = 0.13) +
  geom_line() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = c(0.75, 0.3)) +
  xlab("Spring Extreme Temperature") + ylab("Daily Nest Survival Probability") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
ggsave("nest_survival/output/figures/spring_extreme_temp.jpg",width = 8, height = 6, dpi = 220)


###Spring extreme wind
spwfc <- find.covariates(topmodel, spei_data)
spwfc$value[c(741:764, 815:838)] <- 1:24

###assign sxt values 0:7
#spwfc$value[c(1:74, 75:148)] <- seq(0, 7, length = 74)

###assign sxw values 0:5
spwfc$value[c(149:222, 223:296)] <- seq(0, 5, length = 74)

###create a design matrix with the values you just changed above
spwdesign <- fill.covariates(topmodel, spfc)

###Obtain real estimates
spw.survival <- compute.real(topmodel, design = spdesign)

###Insert number spring extremes
spw.survival$spring_extreme[c(1:74, 75:148)] <- seq(0, 5, length = 74)

###Add site for group variable
spw.survival$Site[1:74] <- ("Kigigak Island")
spw.survival$Site[75:148] <- ("Utqia치vik")

###Change column names
colnames(sp.survival) <- c("dsr", "se", "lci", "uci","fixed", "spring_extreme_wind", "Site")

###Make site a factor variable
is.factor(sp.survival$Site)
sp.survival$site<-as.factor(sp.survival$Site)
is.factor(sp.survival$Site) #now a factor variable

ggplot(sp.survival, aes(x = spring_extreme_wind, y = dsr, color = Site)) +
  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = 0.13) +
  geom_line() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = c(0.75, 0.3)) +
  xlab("Spring Extreme Wind") + ylab("Daily Nest Survival Probability") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
ggsave("nest_survival/output/figures/spring_extreme_wind.jpg",width = 8, height = 6, dpi = 220)


##Create a new dataframe of the nest initiation date values prior to making a graph
ifc <- find.covariates(topmodel, spei_data)

###assign 1:24 for nestages on both sites
ifc$value[c(741:764, 815:838)] <- 1:24

###assign nest initiation date range
ifc$value[c(593:666, 667:740)] <- seq(128, 187, length = 74)

###create a design matrix with the values you just changed above
idesign <- fill.covariates(topmodel, ifc)

###Obtain real estimates
init.survival <- compute.real(topmodel, design = idesign)

###Insert number of high ice days
init.survival$Init[c(1:74, 75:148)] <- seq(128, 187, length = 74)

###Add site for group variable
init.survival$site[1:74] <- ("Kigigak Island")
init.survival$site[75:148] <- ("Utqia치vik")

###Change column names
colnames(init.survival) <- c("dsr", "se", "lci", "uci","fixed", "init", "Site")

###Make site a factor variable
is.factor(init.survival$Site)
init.survival$Site<-as.factor(init.survival$Site)
is.factor(init.survival$Site) #now a factor variable


###Graph 


ggplot(init.survival, aes(x = init, y = dsr, color = Site)) +
  geom_ribbon(aes(ymin = lci, ymax = uci), alpha = 0.13) +
  geom_line() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = c(0.75, 0.3)) +
  xlab("Nest Initiation Date") + ylab("Daily Nest Survival Probability") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
ggsave("nest_survival/output/figures/nest_initiation_date.jpg",width = 8, height = 6, dpi = 220)
```

Calculate nest survival (cumulative dsr)

```{r calculate nest survival}
#######################################################
######Work with stage 1 best model to get overall 24 day cumulative nest success.


###Use find.covariates to get dataframe of mean individual covariates
firstmodel <- model.resultst$S.sxy.in
ffc <- find.covariates(firstmodel, spei_data)

###Build a design matrix for nest ages 1:24, which is the incubation period until hatch for Specs
###1:24 are ages for specs. the following code assign's ages 1:24 for nest age for each year/site
#fc <- find.covariates(final_top_model, spei_data)
ffc$value[2517:2540] <- 1:24 #1994, assign nest ages 1:24 for mean covariate values of nest ages 1:24
ffc$value[2591:2614] <- 1:24 #1995, we start at a huge number but cinit was first computed
ffc$value[2665:2688] <- 1:24 #1996
ffc$value[2739:2762] <- 1:24 #1997
ffc$value[2813:2836] <- 1:24 #1998
ffc$value[2887:2910] <- 1:24 #1999
ffc$value[2961:2984] <- 1:24 #2000
ffc$value[3035:3058] <- 1:24 #2001
ffc$value[3109:3132] <- 1:24 #2002
ffc$value[3183:3206] <- 1:24 #2003
ffc$value[3257:3280] <- 1:24 #2004
ffc$value[3331:3354] <- 1:24 #2005
ffc$value[3405:3428] <- 1:24 #2006
ffc$value[3479:3502] <- 1:24 #2007
ffc$value[3553:3576] <- 1:24 #2008
ffc$value[3627:3650] <- 1:24 #2009
ffc$value[3701:3724] <- 1:24 #2010
ffc$value[3775:3798] <- 1:24 #2011
ffc$value[3849:3872] <- 1:24 #2012
ffc$value[3923:3946] <- 1:24 #2013
ffc$value[3997:4020] <- 1:24 #2014
ffc$value[4071:4094] <- 1:24 #2015
ffc$value[4145:4168] <- 1:24 #2019
ffc$value[4219:4242] <- 1:24 #2021
ffc$value[4293:4316] <- 1:24 #u2010 the 'u-' stands for site "utq"
ffc$value[4367:4390] <- 1:24 #u2011
ffc$value[4441:4464] <- 1:24 #u2012
ffc$value[4515:4538] <- 1:24 #u2013
ffc$value[4589:4612] <- 1:24 #u2014
ffc$value[4663:4686] <- 1:24 #u2015
ffc$value[4737:4760] <- 1:24 #u2016
ffc$value[4811:4834] <- 1:24 #u2017
ffc$value[4885:4908] <- 1:24 #u2018
ffc$value[4959:4982] <- 1:24 #u2019

###fill design matrix with values  of interest that we just changed above.
fdesign <- fill.covariates(firstmodel, ffc)
```
Use the delta method to calculate confidence intervals around annual estimates of nest survival

```{r delta method}
###extract the 1st 24 nest ages for each year from design matrix
ffull.survival <- compute.real(firstmodel, design = fdesign, vcv = TRUE)
freal <- ffull.survival$real
vcv <- ffull.survival$vcv.real


###the function deltamethod.special computes delta-method std errors.
###After you run the function you will get sqrt of the variance.
###to get variance you just square that value

###these codes below will now get the s.
s1994 <- deltamethod.special("prod",ffull.survival$real[1:24],ffull.survival$vcv.real[1:24,1:24])
s1995 <- deltamethod.special("prod",ffull.survival$real[75:98],ffull.survival$vcv.real[75:98,75:98])                                                                                    
s1996 <- deltamethod.special("prod",ffull.survival$real[149:172],ffull.survival$vcv.real[149:172,149:172])
s1997 <- deltamethod.special("prod",ffull.survival$real[223:246],ffull.survival$vcv.real[223:246,223:246])
s1998 <- deltamethod.special("prod",ffull.survival$real[297:320],ffull.survival$vcv.real[297:320,297:320])
s1999 <- deltamethod.special("prod",ffull.survival$real[371:394],ffull.survival$vcv.real[371:394,371:394])
s2000 <- deltamethod.special("prod",ffull.survival$real[445:468],ffull.survival$vcv.real[445:468,445:468])
s2001 <- deltamethod.special("prod",ffull.survival$real[519:542],ffull.survival$vcv.real[519:542,519:542])
s2002 <- deltamethod.special("prod",ffull.survival$real[593:616],ffull.survival$vcv.real[593:616,593:616])
s2003 <- deltamethod.special("prod",ffull.survival$real[667:690],ffull.survival$vcv.real[667:690,667:690])
s2004 <- deltamethod.special("prod",ffull.survival$real[741:764],ffull.survival$vcv.real[741:764,741:764])
s2005 <- deltamethod.special("prod",ffull.survival$real[815:838],ffull.survival$vcv.real[815:838,815:838])
s2006 <- deltamethod.special("prod",ffull.survival$real[889:912],ffull.survival$vcv.real[889:912,889:912])
s2007 <- deltamethod.special("prod",ffull.survival$real[963:986],ffull.survival$vcv.real[963:986,963:986])
s2008 <- deltamethod.special("prod",ffull.survival$real[1037:1060],ffull.survival$vcv.real[1037:1060,1037:1060])
s2009 <- deltamethod.special("prod",ffull.survival$real[1111:1134],ffull.survival$vcv.real[1111:1134,1111:1134])
s2010 <- deltamethod.special("prod",ffull.survival$real[1185:1208],ffull.survival$vcv.real[1185:1208,1185:1208])
s2011 <- deltamethod.special("prod",ffull.survival$real[1259:1282],ffull.survival$vcv.real[1259:1282,1259:1282])
s2012 <- deltamethod.special("prod",ffull.survival$real[1333:1356],ffull.survival$vcv.real[1333:1356,1333:1356])
s2013 <- deltamethod.special("prod",ffull.survival$real[1407:1430],ffull.survival$vcv.real[1407:1430,1407:1430])
s2014 <- deltamethod.special("prod",ffull.survival$real[1481:1504],ffull.survival$vcv.real[1481:1504,1481:1504])
s2015 <- deltamethod.special("prod",ffull.survival$real[1555:1578],ffull.survival$vcv.real[1555:1578,1555:1578])
s2019 <- deltamethod.special("prod",ffull.survival$real[1629:1652],ffull.survival$vcv.real[1629:1652,1629:1652])
s2021 <- deltamethod.special("prod",ffull.survival$real[1703:1726],ffull.survival$vcv.real[1703:1726,1703:1726])
s2010u <- deltamethod.special("prod",ffull.survival$real[1777:1800],ffull.survival$vcv.real[1777:1800,1777:1800])
s2011u <- deltamethod.special("prod",ffull.survival$real[1851:1874],ffull.survival$vcv.real[1851:1874,1851:1874])
s2012u <- deltamethod.special("prod",ffull.survival$real[1925:1948],ffull.survival$vcv.real[1925:1948,1925:1948])
s2013u <- deltamethod.special("prod",ffull.survival$real[1999:2022],ffull.survival$vcv.real[1999:2022,1999:2022])
s2014u <- deltamethod.special("prod",ffull.survival$real[2073:2096],ffull.survival$vcv.real[2073:2096,2073:2096])
s2015u <- deltamethod.special("prod",ffull.survival$real[2147:2170],ffull.survival$vcv.real[2147:2170,2147:2170])
s2016u <- deltamethod.special("prod",ffull.survival$real[2221:2244],ffull.survival$vcv.real[2221:2244,2221:2244])
s2017u <- deltamethod.special("prod",ffull.survival$real[2295:2318],ffull.survival$vcv.real[2295:2318,2295:2318])
s2018u <- deltamethod.special("prod",ffull.survival$real[2369:2392],ffull.survival$vcv.real[2369:2392,2369:2392])
s2019u <- deltamethod.special("prod",ffull.survival$real[2443:2466],ffull.survival$vcv.real[2443:2466,2443:2466])

###Obtain the the dsr estimates for nest ages 1:24
survival.24 <- compute.real(firstmodel, design = fdesign)[c(1:24,
                                                                75:98,
                                                                149:172,
                                                                223:246,
                                                                297:320,
                                                                371:394,
                                                                445:468,
                                                                519:542,
                                                                593:616,
                                                                667:690,
                                                                741:764,
                                                                815:838,
                                                                889:912,
                                                                963:986,
                                                                1037:1060,
                                                                1111:1134,
                                                                1185:1208,
                                                                1259:1282,
                                                                1333:1356,
                                                                1407:1430,
                                                                1481:1504,
                                                                1555:1578,
                                                                1629:1652,
                                                                1703:1726,
                                                                1777:1800,
                                                                1851:1874,
                                                                1925:1948,
                                                                1999:2022,
                                                                2073:2096,
                                                                2147:2170,
                                                                2221:2244,
                                                                2295:2318,
                                                                2369:2392,
                                                                2443:2466), ]

###Get the product of the 24 nest ages to get cumulative nest success probability
###There should be 34 of this. 24 for kigigak island, 10 for Utqiagvik.
product1994 <- prod(survival.24$estimate[1:24]) #1
product1995 <- prod(survival.24$estimate[25:48]) #2
product1996 <- prod(survival.24$estimate[49:72]) #3
product1997 <- prod(survival.24$estimate[73:96]) #4
product1998 <- prod(survival.24$estimate[97:120]) #5
product1999 <- prod(survival.24$estimate[121:144]) #6
product2000 <- prod(survival.24$estimate[145:168]) #7
product2001 <- prod(survival.24$estimate[169:192]) #8
product2002 <- prod(survival.24$estimate[193:216]) #9
product2003 <- prod(survival.24$estimate[217:240]) #10
product2004 <- prod(survival.24$estimate[241:264]) #11
product2005 <- prod(survival.24$estimate[265:288]) #12
product2006 <- prod(survival.24$estimate[289:312]) #13
product2007 <- prod(survival.24$estimate[313:336]) #14
product2008 <- prod(survival.24$estimate[337:360]) #15
product2009 <- prod(survival.24$estimate[361:384]) #16
product2010 <- prod(survival.24$estimate[385:408]) #17
product2011 <- prod(survival.24$estimate[409:432]) #18
product2012 <- prod(survival.24$estimate[433:456]) #19
product2013 <- prod(survival.24$estimate[457:480]) #20
product2014 <- prod(survival.24$estimate[481:504]) #21
product2015 <- prod(survival.24$estimate[505:528]) #22
product2019 <- prod(survival.24$estimate[529:552]) #23
product2021 <- prod(survival.24$estimate[553:576]) #24
product2010u <- prod(survival.24$estimate[577:600]) #25
product2011u <- prod(survival.24$estimate[601:624]) #26
product2012u <- prod(survival.24$estimate[625:648]) #27
product2013u <- prod(survival.24$estimate[649:672]) #28
product2014u <- prod(survival.24$estimate[673:696]) #29
product2015u <- prod(survival.24$estimate[697:720]) #30
product2016u <- prod(survival.24$estimate[721:744]) #31
product2017u <- prod(survival.24$estimate[745:768]) #32
product2018u <- prod(survival.24$estimate[769:792]) #33
product2019u <- prod(survival.24$estimate[793:816]) #34


###create a dataframe of the products of the 24 nest ages above

probsuccess <- c(product1994,product1995,product1996,product1997,product1998,product1999,product2000,
                 product2001,product2002,product2003,product2004,product2005,product2006,product2007,
                 product2008,product2009,product2010,product2011,product2012,product2013,product2014,
                 product2015,product2019,product2021,product2010u,product2011u,product2012u,product2013u,
                 product2014u,product2015u,product2016u,product2017u,product2018u,product2019u)
probsuccess <- as.data.frame(probsuccess)


###create data frame for the square-root of the variance for each year and site
sqrt_s <- c(s1994,s1995,s1996,s1997,s1998,s1999,s2000,s2001,
            s2002,s2003,s2004,s2005,s2006,s2007,s2008,s2009,s2010,
            s2011,s2012,s2013,s2014,s2015,s2019,s2021,s2010u,s2011u,
            s2012u,s2013u,s2014u,s2015u,s2016u,s2017u,s2018u,s2019u)
sqrt_s <- as.data.frame(sqrt_s)

###combine probsuccess and sqrt_s to get a dataframe where you can work with to get lower and upper CI
data <- cbind(probsuccess,sqrt_s)
data$lci <- data$probsuccess - 1.96*(data$sqrt_s/sqrt(24))
data$uci <- data$probsuccess + 1.96*(data$sqrt_s/sqrt(24))
```

Plot nest survival estimates

```{r plot nest survival with CIs}
####YOU CAN FINALLY PLOT THIS DAMN FIGURE####

###Add site and year to data frame
data$site <- c("kig","kig","kig","kig","kig","kig",
               "kig","kig","kig","kig","kig","kig",
               "kig","kig","kig","kig","kig","kig",
               "kig","kig","kig","kig","kig","kig",
               "utq","utq","utq","utq","utq",
               "utq","utq","utq","utq","utq")

data$year <- c("1994","1995","1996","1997","1998","1999",
               "2000","2001","2002","2003","2004","2005",
               "2006","2007","2008","2009","2010","2011",
               "2012","2013","2014","2015","2019","2021",
               "2010","2011","2012","2013","2014",
               "2015","2016","2017","2018","2019")


data$probsuccess<-as.numeric(data$probsuccess)
###plot
ggplot(data, aes(x = year, y = probsuccess, color = site)) +
  #geom_ribbon(aes(ymin = lcl, ymax = ucl), alpha = 0.13) +
  geom_errorbar(aes(ymin = lci, ymax = uci, width = 0.4)) +
  geom_point() +
  geom_hline(yintercept = mean(data$probsuccess[1:24]), color = "red", lty = "dashed") +
  geom_hline(yintercept = mean(data$probsuccess[25:34]), color = "blue", lty = "dashed") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = c(0.75, 0.3)) +
  xlab("Year") + ylab("cumuluative nest succes (24-day)") +
  theme_bw() +
  theme(
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  ) +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
ggsave("nest_survival/output/figures/nest_success_prob.jpg",width = 8, height = 6, dpi = 220)


###Average nest success probability between sites
kignestsuccess <- mean(data$probsuccess[1:24]) ##0.674130129
utqnestsuccess <- mean(data$probsuccess[25:34]) ##0.7461755994

```

Nest survival at Kigigak was `r kignestsuccess`.

Nest survival at Utqiagvil was `r utqnestsuccess`

